Inferring probabilistic stellar rotation periods using Gaussian processes

### 2017-02-13 documents/ms.tex
minor edit

The flexibility of this GP model allows for posterior multimodality and 
``over-fitting''--like behavior. 
For example, if $l$ is small, the non-periodic factor in the covariance
kernel may dominate, allowing for a good fit to the data without
requiring any periodic covariance structure---even if clear periodic
structure is present.
Additionally, if $\Gamma$ is too large, the GP model becomes extremely
flexible and can fit the data without varying the period.

@@

We do not attempt to decide which single
peak in the ACF best represents the true rotation period,
but rather we identify several \emph{candidate} periods and define
a weighting scheme in order to create a non-commital, though useful,
multimodal prior.  While this procedure does not avoid heuristic choices,
the fact that its goal is simply to create a \emph{prior} for a
probabilitistically justified inference scheme rather than
to identify a single correct period softens the potential impact
of these choices.

>>>>

The flexibility of this GP model allows for posterior multimodality and 
``over-fitting''--like behavior. 
For example, if $l$ is small, the non-periodic factor in the covariance
kernel may dominate, allowing for a good fit to the data without
requiring any periodic covariance structure---even if clear periodic
structure is present.
Additionally, for large values of $\Gamma$ the GP model becomes extremely
flexible and can fit the data without varying the period.

@@

We do not attempt to decide which single
peak in the ACF best represents the true rotation period,
but rather we identify several \emph{candidate} periods and define
a weighting scheme in order to create a non-commital, though useful,
multimodal prior.  While this procedure does not avoid heuristic choices,
we soften the potential impact of these choices because we are simply
creating a \emph{prior} for probabilistically justified
inference rather attempting to identify a single correct period.
